<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2014-09-03 ants2015build.Rmd
WIP: regular update

## Network visualization
see `?plotBasicNetwork`
```{r networkfn,results='hide',warning=FALSE,echo=FALSE,message=FALSE}
ofn<-paste(figpath,'network',sep='')
ofnpng<-paste(ofn,'.png',sep='')
```
```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=T}
       mnit<-getANTsRData("mni")
       mnit<-antsImageRead(mnit,3)
       mnia<-getANTsRData("mnia")
       mnia<-antsImageRead(mnia,3)
       ThresholdImage(3,mnit,mnit,1,max(mnit))
       ImageMath(3,mnit,"FillHoles",mnit)
       cnt<-getCentroids( mnia, clustparam = 50 )
       aalcnt<-cnt$centroids[1:90,]
       brain<-renderSurfaceFunction( surfimg =list( mnit ) , alphasurf=0.1 ,smoothsval = 1.5 )
       testweights<-matrix( rep( 0, 90*90 ) ,nrow=90)
       testweights[31,37]<-1  # ant cingulate to hipp
       testweights[31,36]<-2  # ant cingulate to post cingulate
       testweights[11,65]<-3  # broca to angular 
       plotBasicNetwork( centroids = aalcnt , brain , weights=testweights )
       id<-par3d("userMatrix")
       rid<-rotate3d( id , -pi/2, 1, 0, 0 )
       rid2<-rotate3d( id , pi/2, 0, 0, 1 )
       rid3<-rotate3d( id , -pi/2, 0, 0, 1 )
       par3d(userMatrix = id ) 
       dd<-make3ViewPNG(  rid, id, rid2,  ofn )
       par3d(userMatrix = id ) 
```
![](`r ofnpng`)

>>>>

## Network visualization
see `?plotBasicNetwork`
```{r networkfn,results='hide',warning=FALSE,echo=FALSE,message=FALSE}
ofn<-paste(figpath,'network',sep='')
ofnpng<-paste(ofn,'.png',sep='')
```
```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=F}
       mnit<-getANTsRData("mni")
       mnit<-antsImageRead(mnit,3)
       mnia<-getANTsRData("mnia")
       mnia<-antsImageRead(mnia,3)
       ThresholdImage(3,mnit,mnit,1,max(mnit))
       ImageMath(3,mnit,"FillHoles",mnit)
       cnt<-getCentroids( mnia, clustparam = 50 )
       aalcnt<-cnt$centroids[1:90,]
       brain<-renderSurfaceFunction( surfimg =list( mnit ) , alphasurf=0.1 ,smoothsval = 1.5 )
       testweights<-matrix( rep( 0, 90*90 ) ,nrow=90)
       testweights[31,37]<-1  # ant cingulate to hipp
       testweights[31,36]<-2  # ant cingulate to post cingulate
       testweights[11,65]<-3  # broca to angular 
       plotBasicNetwork( centroids = aalcnt , brain , weights=testweights )
       id<-par3d("userMatrix")
       rid<-rotate3d( id , -pi/2, 1, 0, 0 )
       rid2<-rotate3d( id , pi/2, 0, 0, 1 )
       rid3<-rotate3d( id , -pi/2, 0, 0, 1 )
       par3d(userMatrix = id ) 
       dd<-make3ViewPNG(  rid, id, rid2,  ofn )
       par3d(userMatrix = id ) 
```
![](`r ofnpng`)
